### 2021-05-13 code/manuscript.Rmd
add average tfr

# Re-run preprocessing and/or model fitting?
rerun_preprocessing <- TRUE
rerun_model_fitting <- TRUE
```

@@

```{r, preprocessing}
# Define ERP components of interest
erp_components <- tibble(
  name = c("P1", "N170", "N400"),
  tmin = c(0.1, 0.15, 0.4),
  tmax = c(0.15, 0.2, 0.7),
  roi = list(
    c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
    c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
    c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
  )
)

# Define frequencies and # of cycles for TFR analysis
tfr_freqs <- seq(4, 50, by = 2)
tfr_cycles <- seq(3, 10, length.out = length(tfr_freqs))

# Run the preprocessing if requested (only works if the raw data are available)
if (rerun_preprocessing) {

  # List EEG files and behavioral log files
  fname_vhdr <- c(
    list.files("data/raw/eeg/exp1", pattern = ".vhdr", full.names = TRUE),
    list.files("data/raw/eeg/exp2", pattern = ".vhdr", full.names = TRUE)
  )
  fname_log <- c(
    list.files("data/raw/rt/exp1", pattern = ".txt", full.names = TRUE),
    list.files("data/raw/rt/exp2", pattern = ".txt", full.names = TRUE)
  )

  # Generate new BIDS-style subject IDs
  1:length(fname_vhdr) %>%
    str_pad(width = 2, pad = 0) %>%
    paste0("sub-", .) -> subject_id

  # Perform preprocessing for all subjects using MNE-Python (see code/preprocessing.py)
  tibble(fname_vhdr, fname_log, subject_id) %>%
    pwalk(
      pp$preprocess,
      output_dir = "data/preprocessed",
      eog_names = c("HEOG", "VEOG"),
      eog_anodes = c("F9", "Auge_u"),
      eog_cathodes = c("F10", "Fp1"),
      montage_kind = "easycap-M1",
      ica_components = as.integer(15),
      ica_method = "fastica",
      ica_seed = as.integer(1234),
      hipass = 0.1,
      lowpass = 30,
      event_id = dict(match = as.integer(221), mismatch = as.integer(222)),
      tmin = -0.5,
      tmax = 1.489,
      baseline = tuple(-0.2, 0),
      reject = dict(eeg = 200e-6),
      erp_components = erp_components,
      condition_cols = c("part", "condition"),
      tfr_freqs = tfr_freqs,
      tfr_cycles = tfr_cycles,
      tfr_sfreq_downsampled = 250,
      tfr_crop = tuple(-0.2, 0.8)
    )
}

please_stop_here()
```

```{r, preprocessing_old}
# Define ERP components of interest
comps <- tibble(
  name = c("P1", "N170", "N400"),
  tmin = c(100, 150, 400),
  tmax = c(150, 200, 700),
  roi = list(
    c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
    c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
    c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
  )
)

# Define some filenames for I/O
fnames <- list(
  epochs = "data/processed/aha-epo.fif",
  epochs_unf = "data/processed/aha-unf-epo.fif",
  trials = "data/processed/aha-trials.csv",
  gavgs = "data/processed/aha-gavgs.RDS",
  conditions = "data/processed/aha-obj-per-cond.csv",
  montage = "data/processed/aha-montage.csv",
  models_freq = "data/processed/aha-models-freq.RDS"
)

# Define parameters for EEG preprocessing
preproc_params <- list(
  # Number of ICA components
  n_components = as.integer(15),
  # ICA methods
  method = "fastica",
  # Lower edge of pass-band filter
  l_freq = 0.1,
  # Upper edge of pass-band filter
  h_freq = 30,
  # Event trigger codes
  event_id = dict(match = as.integer(221), mismatch = as.integer(222)),
  # Beginning of epochs in s
  tmin = -0.5,
  # End of epochs in s
  tmax = 1.498,
  # Baseline interval in s
  baseline = tuple(-0.2, 0),
  # Artifact rejection threshold in microvolts
  reject = dict(eeg = 200)
)

# Check if single-trial data are available
if (file.exists(fnames$trials)) {

  # If so, load preprocessed single-trial data
  read_tsv(fnames$trials, col_types = cols()) %>%

    # Factorize columns
    mutate(
      part = factor(part, levels = c("I", "II", "III")),
      condition = factor(condition, levels = c(
        "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
      )),
      participant = factor(participant),
      item = factor(item)
    ) -> aha

} else {

  # If not, we preprocess the behvarioral and EEG data
  paste0("data/raw/rt/exp", 1:2) %>%
    map(list.files, pattern = ".txt", full.names = TRUE) %>%
    map(map, function(txt_fname) {

      # Read the behavioral log file
      suppressWarnings(read_tsv(txt_fname, col_types = cols())) %>%

        # Rename columns for participant and item IDs
        rename(participant = VPNummer, item = StimID) %>%

        # Add a column for the part of the experiment
        mutate(part = case_when(
          Wdh %in% c(211, 231) ~ "I",
          Wdh %in% c(212, 232) ~ "II",
          Wdh %in% c(213, 233) ~ "III",
          Wdh == 234 ~ "IV"
        ) %>% as_factor()) %>%

        # Remove filler stimuli (i.e.,well-known objects)
        filter(bek_unbek != "bekannt") -> dat

      # Assign stimuli to conditions based on keywords and button presses in Part II
      excl_known <- dat %>%
        filter(part == "I" & Tastencode == 201) %>%
        pull(item)
      excl_informed <- dat %>%
        filter(part == "II" & Bed == "richtig" & !Tastencode %in% c(201, 202)) %>%
        pull(item)
      excl_naive <- dat %>%
        filter(part == "II" & Bed == "falsch" & !Tastencode %in% c(203, 204)) %>%
        pull(item)
      informed <- dat %>%
        filter(part == "II" & Bed == "richtig" & Tastencode %in% c(201, 202)) %>%
        pull(item)
      naive <- dat %>%
        filter(part == "II" & Bed == "falsch" & Tastencode %in% c(203, 204)) %>%
        pull(item)

      # Create a new condition for these experimental condition
      dat %<>% mutate(condition = case_when(
        item %in% excl_known ~ "Excl_known",
        item %in% excl_informed ~ "Excl_informed",
        item %in% excl_naive ~ "Excl_naive",
        item %in% informed ~ "Informed",
        item %in% naive ~ "Naive"
      ) %>% factor(levels = c(
        "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
      ))) %>%

        # Return only relevant columns
        select(part, condition, participant, item, RT) %>%
        return()
    }) -> behav

  # Avoid duplicate participant labels across the two experiments
  behav[[2]] %<>% map(mutate, participant = paste0(participant, "_2"))

  # Merge behavioral data for all participants into a single list
  behav %<>% flatten()

  # List BrainVision header file names for preprocessing
  paste0("data/raw/eeg/exp", 1:2) %>%
    list.files(pattern = ".vhdr", full.names = TRUE) -> fnames$vhdr

  # # Do the actual preprocessing in MNE-Python
  # exec(
  #   .fn = py$preproc_all,
  #   vhdr_fnames = fnames$vhdr,
  #   metadatas = behav,
  #   output_fname = fnames$epochs,
  #   !!!preproc_params
  # ) -> epochs
  # 
  # # Compute mean ERP amplitudes and bind to the behavioral data
  # pmap_dfc(comps, py$compute_erps, epochs_fname = fnames$epochs) %>%
  #   set_names(comps$name) %>%
  #   bind_cols(epochs$metadata, .) %T>%
  #   write_tsv(fnames$trials) -> aha
  # 
  # # Compute grand averages per part and condition
  # py$compute_evokeds(epochs_fname = fnames$epochs, grand = TRUE, data_only = TRUE) %>%
  #   saveRDS(fnames$gavgs)
  # 
  # # Backup number of stimuli assigned to each condition for all participants
  # map(behav, function(x) table(x$condition) / 3) %>%
  #   bind_rows() %>%
  #   mutate(Participant = unique(aha$participant), .before = 1) %>%
  #   write_csv(fnames$conditions)
  # 
  # # Get standard EasyCap electrode positions and project to 2D space
  # py$mne$channels$`_standard_montage_utils`$MONTAGE_PATH %>%
  #   list.files(pattern = "easycap-M1.txt", full.names = TRUE) %>%
  #   read_tsv(col_types = cols()) %>%
  #   rename(electrode = Site) %>%
  #   inner_join(tibble(electrode = epochs$ch_names), ., by = "electrode") %>%
  #   mutate(
  #     x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
  #     y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
  #   ) %>%
  #   write_csv(fnames$montage)

  # Do the preprocessing again, this time without filtering (for TFR)
  preproc_params$l_freq <- py_none()
  preproc_params$h_freq <- py_none()
  preproc_params$reject <- py_none()
  exec(
    .fn = py$preproc_all,
    vhdr_fnames = fnames$vhdr,
    metadatas = behav,
    output_fname = fnames$epochs_unf,
    !!!preproc_params
  ) -> epochs_unf
}

# Check number of rejected epochs
aha %>%
  group_by(participant) %>%
  tally() %>%
  mutate(n = 360 - n) %>%
  pull(n) -> rejected
mean(rejected)    # Mean
median(rejected)  # Median
range(rejected)   # Range
```

```{r, models_freq}
# Remove any trials excluded from conditions
aha %>%
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> aha

@@

```{python, tfr}
from mne.time_frequency import tfr_morlet
from mne.channels import find_ch_adjacency
from mne.stats import spatio_temporal_cluster_test

epochs_unf = mne.read_epochs(r.fnames["epochs_unf"])
epochs_ptII_informed = epochs_unf["part == 'II' & condition == 'Informed'"]
epochs_ptII_naive = epochs_unf["part == 'II' & condition == 'Naive'"]

evokeds = compute_evokeds(
  epochs_fname=r.fnames["epochs_unf"], grand=False, data_only=False
  )

  evokeds_informed = evokeds["II"]["Informed"]
  evokeds_naive = evokeds["II"]["Naive"]

  X1 = np.array([evokeds.data for evokeds in evokeds_informed])
  X2 = np.array([evokeds.data for evokeds in evokeds_naive])
  X1 = np.transpose(X1, [0, 2, 1])
  X2 = np.transpose(X2, [0, 2, 1])
  X = [X1, X2]

  adjacency, ch_names = find_ch_adjacency(evokeds["II"]["Informed"][0].info, ch_type="eeg")

  cluster_stats = spatio_temporal_cluster_test(
    X=X,
    n_permutations=1000,
    tail=0,
    n_jobs=1,
    buffer_size=None,
    adjacency=adjacency,
    )

    p_accept = 0.05
    T_obs, clusters, p_values, _ = cluster_stats
    good_cluster_inds = np.where(p_values < p_accept)[0]

    freqs = np.logspace(*np.log10([6, 35]), num=8)
    n_cycles = freqs / 2.

    tfr_ptII_informed = tfr_morlet(
      epochs_ptII_informed,
      freqs=freqs,
      n_cycles=n_cycles,
      decim=2,
      return_itc=False,
      average=False,
      )
      tfr_ptII_naive = tfr_morlet(
        epochs_ptII_naive,
        freqs=freqs,
        n_cycles=n_cycles,
        decim=2,
        return_itc=False,
        average=False,
        )

        tfr_ptII_informed.apply_baseline(mode='ratio', baseline=(None, 0))
        tfr_ptII_naive.apply_baseline(mode='ratio', baseline=(None, 0))

        adjacency, ch_names = find_ch_adjacency(epochs_ptII_informed.info, ch_type="eeg")

        spatio_temporal_cluster_test(X, n_permutations=1000,
        threshold=threshold, tail=1,
        n_jobs=1, buffer_size=None,
        adjacency=adjacency)

        ```

        ```{python tfr_old, eval=FALSE}
        import mne
        import numpy as np
        #import matplotlib.pyplot as plt

        # epochs = preproc(
        #   vhdr_fname="data/exp1/eeg/Vp0004.vhdr",
        #   metadata=r.aha.query("participant == 'VP_04'"),
        #   n_components=15,
        #   method="fastica",
        #   l_freq=None,
        #   h_freq=None,
        #   event_id=dict(match=221, mismatch=222),
        #   tmin=-0.5,
        #   tmax=1.498,
        #   baseline=(-0.2, 0),
        #   reject=dict(eeg=200)
        # )
        # epochs.save("data/processed/vp04-epo.fif")

        epochs = mne.read_epochs("data/processed/unf-exp1-epo.fif")

        evokeds = compute_evokeds(epochs_c, grand=True, data_only=False)
        evokeds_i = evokeds["II"]["Informed"]
        evokeds_n = evokeds["II"]["Naive"]

        freqs = np.logspace(*np.log10([6, 35]), num=8)
        n_cycles = freqs / 2.
        power_i = mne.time_frequency.tfr_morlet(evokeds_i, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True, n_jobs=1)
        power_n = mne.time_frequency.tfr_morlet(evokeds_n, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True, n_jobs=1)
        power_i = power_i.apply_baseline(mode='mean', baseline=(-.400, -.100))
        power_n = power_n.apply_baseline(mode='mean', baseline=(-.400, -.100))

        power_d = power_i.copy()
        power_d.data = power_i.data - power_n.data

        power_d.plot()

        # epochs.resample(250., npad='auto')

        roi = r.comps["roi"][0] + r.comps["roi"][1]
        idxs = np.where(np.in1d(epochs.ch_names, roi))

        epochs_i = epochs["part == 'II' & condition == 'Informed'"].pick_channels(roi)
        epochs_n = epochs["part == 'II' & condition == 'Naive'"].pick_channels(roi)

        epochs_c = mne.channels.combine_channels(epochs, groups=dict(avg=range(62)))

        epochs_c.metadata = epochs.metadata
        epochs_s = epochs_c["part == 'II'"]
        # epochs_i = epochs_s["condition == 'Informed'"]
        # epochs_n = epochs_s["condition == 'Naive'"]

        # power_i = mne.time_frequency.tfr_morlet(epochs_i, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True, n_jobs=1)
        # power_n = mne.time_frequency.tfr_morlet(epochs_n, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True, n_jobs=1)
        # power_d = power_i - power_n
        # 
        # power_d.plot([0], baseline=(-0.5, 0), mode='percent', vmin=-1, vmax=1)

        # define frequencies of interest (log-spaced)
        #freqs = np.logspace(*np.log10([6, 35]), num=8)
        freqs = np.arange(3, 50, 1.6)
        #n_cycles = freqs / 2.  # different number of cycle per frequency
        n_cycles = np.linspace(3, 10, len(freqs))
        power = mne.time_frequency.tfr_morlet(epochs_c, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True, n_jobs=1)

        power.plot([0], baseline=(-0.5, 0), mode='percent')

        power.plot_topo(baseline=(-0.5, 0), mode='logratio')
        power.plot_topomap(ch_type='eeg', tmin=0.15, tmax=0.2, fmin=8, fmax=12, baseline=(-0.5, 0), mode='logratio', title='Alpha')
        power.plot_topomap(ch_type='eeg', tmin=0.15, tmax=0.2, fmin=13, fmax=25, baseline=(-0.5, 0), mode='logratio', title='Beta')

        import numpy as np
        import matplotlib.pyplot as plt
        from mne.baseline import rescale
        from mne.stats import bootstrap_confidence_interval
        iter_freqs = [
          ('Theta', 4, 7),
          ('Alpha', 8, 12),
          ('Beta', 13, 25),
          ('Gamma', 30, 45)
          ]
          raw_fname = "data/exp1/EEG/Vp0004.vhdr"
          tmin, tmax = -0.5, 1.498
          baseline = None
          frequency_map = list()
          event_id = dict(match=222)
          for band, fmin, fmax in iter_freqs:
            # (re)load the data to save memory
            raw = mne.io.read_raw_brainvision(raw_fname, scale=1e6, preload=True)
            raw.filter(fmin, fmax, n_jobs=1,  # use more jobs to speed up.
            l_trans_bandwidth=1,  # make sure filter params are the same
            h_trans_bandwidth=1)  # in each band and skip "auto" option.
            events, _ = mne.events_from_annotations(raw, verbose=False)
            epochs = mne.Epochs(raw, events, event_id, tmin, tmax, baseline=baseline,
            reject=dict(eeg=200), preload=True)
            # remove evoked response
            epochs.subtract_evoked()
            # get analytic signal (envelope)
            epochs.apply_hilbert(envelope=True)
            frequency_map.append(((band, fmin, fmax), epochs.average()))
            del epochs
            del raw
            # Helper function for plotting spread
            def stat_fun(x):
              """Return sum of squares."""
              return np.sum(x ** 2, axis=0)
            # Plot
            fig, axes = plt.subplots(4, 1, figsize=(10, 7), sharex=True, sharey=True)
            colors = plt.get_cmap('winter_r')(np.linspace(0, 1, 4))
            for ((freq_name, fmin, fmax), average), color, ax in zip(
              frequency_map, colors, axes.ravel()[::-1]):
                times = average.times * 1e3
                gfp = np.sum(average.data ** 2, axis=0)
                gfp = mne.baseline.rescale(gfp, times, baseline=(None, 0))
                ax.plot(times, gfp, label=freq_name, color=color, linewidth=2.5)
                ax.axhline(0, linestyle='--', color='grey', linewidth=2)
                ci_low, ci_up = bootstrap_confidence_interval(average.data, random_state=0,
                stat_fun=stat_fun)
                ci_low = rescale(ci_low, average.times, baseline=(None, 0))
                ci_up = rescale(ci_up, average.times, baseline=(None, 0))
                ax.fill_between(times, gfp + ci_up, gfp - ci_low, color=color, alpha=0.3)
                ax.grid(True)
                ax.set_ylabel('GFP')
                ax.annotate('%s (%d-%dHz)' % (freq_name, fmin, fmax),
                xy=(0.95, 0.8),
                horizontalalignment='right',
                xycoords='axes fraction')
                axes.ravel()[-1].set_xlabel('Time [ms]')
                plt.show()
                ```

                ```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
                # Load sample time points and electrode montage
                montage <- read_csv("data/processed/aha-montage.csv", col_types = cols())

>>>>

# Re-run preprocessing and/or model fitting?
rerun_preprocessing <- TRUE
rerun_model_fitting <- TRUE

# File names for easier I/O
fnames <- list(
  montage = "data/processed/montage.csv",
  evo_gavg = "data/processed/evo_gavg.csv",
  evo_tfr_gavg = "data/processed/evo-tfr_gavg.csv",
  evo_tfr_diff = "data/processed/evo-tfr_diff.csv",
  evo_tfr_gavg_nochans = "data/processed/evo-tfr_gavg-nochans.csv",
  evo_tfr_diff_nochans = "data/processed/evo-tfr_diff-nochans.csv"
)
```

@@

```{r, preprocessing}
# List EEG files and behavioral log files
fname_vhdr <- c(
  list.files("data/raw/eeg/exp1", pattern = ".vhdr", full.names = TRUE),
  list.files("data/raw/eeg/exp2", pattern = ".vhdr", full.names = TRUE)
)
fname_log <- c(
  list.files("data/raw/rt/exp1", pattern = ".txt", full.names = TRUE),
  list.files("data/raw/rt/exp2", pattern = ".txt", full.names = TRUE)
)

# Generate new BIDS-style subject IDs
seq(length(fname_vhdr)) %>%
  str_pad(width = 2, pad = 0) %>%
  paste0("sub-", .) -> subject_id

# Define ERP components of interest
erp_components <- tibble(
  name = c("P1", "N170", "N400"),
  tmin = c(0.1, 0.15, 0.4),
  tmax = c(0.15, 0.2, 0.7),
  roi = list(
    c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
    c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
    c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
  )
)

# Define frequencies and number of cycles for TFR analysis
tfr_freqs <- seq(4, 50, by = 2)
tfr_cycles <- seq(3, 10, length.out = length(tfr_freqs))

# Perform preprocessing for all subjects using MNE-Python (see code/preprocessing.py)
# This will run only if `rerun_preprocessing = TRUE` and if the raw data are available
if (rerun_preprocessing) {

  # Do the actual preprocessing
  tibble(fname_vhdr, fname_log, subject_id) %>%
    pwalk(
      pp$preprocess,
      output_dir = "data/preprocessed",
      eog_names = c("HEOG", "VEOG"),
      eog_anodes = c("F9", "Auge_u"),
      eog_cathodes = c("F10", "Fp1"),
      montage_kind = "easycap-M1",
      ica_components = as.integer(15),
      ica_method = "fastica",
      ica_seed = as.integer(1234),
      hipass = 0.1,
      lowpass = 30,
      event_id = dict(match = as.integer(221), mismatch = as.integer(222)),
      tmin = -0.5,
      tmax = 1.489,
      baseline = tuple(-0.2, 0),
      reject = dict(eeg = 200e-6),
      erp_components = erp_components,
      average_by = c("part", "condition", "subject_id"),
      tfr_equalize = "condition == ['Informed', 'Naive']",
      tfr_resample = py_none(),
      tfr_freqs = tfr_freqs,
      tfr_cycles = tfr_cycles,
      tfr_crop = tuple(-0.2, 0.8)
    )

  # Get standard EasyCap electrode positions and project them into 2D space
  read_csv("data/preprocessed/sub-01_tfr-evo.csv", col_types = cols()) %>%
    select(-c(part, condition, subject_id, time, freq)) %>%
    colnames() -> ch_names
  import("mne.channels._standard_montage_utils")$MONTAGE_PATH %>%
    paste0("/easycap-M1.txt") %>%
    read_tsv(col_types = cols()) %>%
    rename(electrode = Site) %>%
    inner_join(tibble(electrode = ch_names), ., by = "electrode") %>%
    mutate(
      x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
      y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
    ) %>%
    mutate(across(c(x, y), round, 3)) %>%
    write_csv(fnames$montage)
}
```

```{python, grand_averaging, eval=rerun_preproc}
from os import makedirs

import numpy as np
import pandas as pd

# Create output folder
makedirs("data/processed", exist_ok=True)

# Read evoked *potentials* for all subjects
fname_evo_tfr = ["data/preprocessed/" + sub + "_evo.csv" for sub in r.subject_id]
evo = [pd.read_csv(fname) for fname in fname_evo_tfr]
evo = pd.concat(evo)

# Average across subjects
id_vars = ["part", "condition", "time"]
evo = evo.groupby(id_vars, as_index=False).mean()
evo.to_csv(r.fnames["evo_gavg"], float_format="%.3f", index=False)

# Read evoked *power* for all subjects
fname_evo_tfr = ["data/preprocessed/" + sub + "_tfr-evo.csv" for sub in r.subject_id]
evo_tfr = [pd.read_csv(fname) for fname in fname_evo_tfr]
evo_tfr = pd.concat(evo_tfr)

# Compute difference in power between conditions
id_vars = ["part", "condition", "subject_id", "time", "freq"]
electrodes = [col for col in evo_tfr.columns if (col not in id_vars)]
evo_tfr_diff = (
    evo_tfr.query("condition == 'Informed'")[electrodes]
    - evo_tfr.query("condition == 'Naive'")[electrodes].values
)
evo_tfr_diff[id_vars] = evo_tfr.query("condition == 'Informed'")[id_vars]

# Average first across subjects, then across electrodes
id_vars.remove("subject_id")
fnames = [r.fnames["evo_tfr_gavg"], r.fnames["evo_tfr_diff"]]
fnames_nochans = [r.fnames["evo_tfr_gavg_nochans"], r.fnames["evo_tfr_diff_nochans"]]
for df, fname, fname_nochans in zip([evo_tfr, evo_tfr_diff], fnames, fnames_nochans):
    df = df.groupby(id_vars, as_index=False).mean()
    df.to_csv(fname, float_format="%.3f", index=False)
    df["power"] = df[electrodes].mean(axis=1)
    df.drop(electrodes, axis=1, inplace=True)
    df.to_csv(fname_nochans, float_format="%.3f", index=False)
del df, evo_tfr, evo_tfr_diff
```

```{r, tfr_wip}
please_stop_here()

# Read evoked power
paste0("data/preprocessed/", subject_id, "_tfr-evo.csv") %>%
  map(read_csv, col_types = cols())

  map2(subject_id, function(fname, id) {
    read_csv(fname, col_types = cols(), progress = FALSE) %>%
      mutate(participant = id)
  }) %>%
  bind_rows() -> evo

# Average across participants
grouping <- c("part", "condition", "time", "freq")
evo %<>%
  group_by(across(all_of(grouping))) %>%
  summarise(across(-participant, .fns = mean), .groups = "drop")

# Average across channels
evo %>%
  pivot_longer(!all_of(grouping), names_to = "channel", values_to = "power") %>%
  group_by(across(all_of(grouping))) %>%
  summarise(power = mean(power), .groups = "drop") -> evo_all_channels

# Average across conditions within parts
evo_all_channels %>%
  group_by(part, time, freq) %>%
  summarise(power = mean(power), .groups = "drop") -> evo_all_channels_conds

# Plot
evo_all_channels_conds %>%
  ggplot(aes(x = time, y = freq, fill = power)) +
  facet_wrap(~part) +
  geom_raster() +
  scale_fill_viridis_c(limits = c(0, 2), oob = scales::squish) +
  annotate("rect", xmin = 150, xmax = 400, ymin = 30, ymax = 50, color = "white", fill = NA) +
  theme(aspect.ratio = 0.5) +
  theme_minimal() +
  coord_cartesian(expand = FALSE) +
  ggsave("evo_all_channels_conds.pdf", width = 7, height = 2)

# Compute differences between conditions
evo_all_channels %>%
  group_by(part, time, freq) %>%
  mutate(power = power - power[condition == "Naive"]) %>%
  filter(condition == "Informed") %>%
  ggplot(aes(x = time, y = freq, fill = power)) +
  facet_wrap(~part) +
  geom_raster() +
  scale_fill_viridis_c(limits = c(0, 1), oob = scales::squish) +
  annotate("rect", xmin = 150, xmax = 400, ymin = 30, ymax = 50, color = "white", fill = NA) +
  theme(aspect.ratio = 0.5) +
  theme_minimal() +
  coord_cartesian(expand = FALSE) +
  ggsave("evo_all_channels_diff.pdf", width = 7, height = 2)
```

```{r, models_freq}
# Read single trial data for all subjects
paste0("data/preprocessed/", subject_id, "_trials.csv") %>%
  map(read_csv, col_types = cols()) %>%
  bind_rows() %>%
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c("Informed", "Naive")),
    subject_id = factor(subject_id),
    item_id = factor(item_id)
  ) %>%
  na.omit() -> trials

contrasts_condition <- t(cbind(c("Informed" = 1, "Naive" = -1)))
contrasts_part <- t(cbind(
  c("I" = -1, "II" = 1, "III" = 0),
  c("I" = 0, "II" = -1, "III" = 1)
))

# Apply these contrasts to the factors in the data
contrasts(trials$condition) <- MASS::ginv(contrasts_condition)
contrasts(trials$part) <- MASS::ginv(contrasts_part)

formula <- N400 ~ part / condition + (1|subject_id) + (1|item_id)
mod <- lmer(formula, data = trials)
summary(mod)

# Remove any trials excluded from conditions
aha %>%
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> aha

@@

```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
# Load montage and data
montage <- read_csv(fnames$montage, col_types = cols())
evokeds <- read_csv(fnames$evo_gavg, col_types = cols())
